### 2015-06-05 Manuscript/Missing_mammals-draft.tex
Edits to results

\section{Results}
In the @@@ cladistic matrices extracted in our searches, @11 out of @28 mammalian orders have a ``low'' coverage (\textless 25\%) of species with cladistic data and @24 have a ``high'' coverage (\textgreater 75\%).
At the genus-level, only @three orders have a ``low'' coverage of taxa with cladistic data and @16 have a ``high'' coverage.
Finally, at the family-level @no order has a ``low'' coverage and only @5 have a ``high'' coverage (Table \ref{Table_morpho_taxa_proportion}).

@@

Among the mammalian orders containing OTUs with no available cladistic data, only @two orders, Carnivora and Chiroptera, are significantly phylogenetically clustered both at the species- and the genus-level (Table~\ref{Table_data_structure}).

@@

Two contrasting results are shown on Figure \ref{Figure_example_coverage} with randomly distributed data in Cetartiodactyla (Figure \ref{Figure_example_coverage}A) and phylogenetically clustered data in Carnivora (mainly Canidae; Figure \ref{Figure_example_coverage}B).

>>>>

\section{Results}
Across the @@@ cladistic matrices we extracted, @11 out of @28 mammalian orders have low coverage (\textless 25\% of species with cladistic data) and @24 have high coverage (\textgreater 75\% of species with cladistic data) at the species-level.
At the genus-level, only @three orders have low coverage of taxa and @16 have high coverage, and at the family-level, @no orders have low coverage and @5 have high coverage (Table \ref{Table_morpho_taxa_proportion}).

@@

Among the mammalian orders containing OTUs with no available cladistic data, only @two orders, Carnivora and Chiroptera, have OTUs with cladistic data that are significantly phylogenetically clustered at the species- and the genus-level (Table~\ref{Table_data_structure}).

@@

Two contrasting results are shown in Figure \ref{Figure_example_coverage} with randomly distributed OTUs with cladistic data in Cetartiodactyla (Figure \ref{Figure_example_coverage}A) and phylogenetically clustered OTUs with cladistic data in Carnivora (mainly Canidae; Figure \ref{Figure_example_coverage}B).
